---
title: "SU20 Summer Individual Courses Ad Campaign"
author: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r}
library(tidyverse)
library(knitr)
library(kableExtra)
library(hms)
library(ggpubr)
```


# Basic Description:

The Office of Marketing and Brand Management at the University of Southern Maine (USM) has been running digital ads promoting summer individual classes via  Google Ads CPC and Facebook and Instagram digital display. The campaign began February 24, 2020 and will run through July 3, 2020, with a 2 week hiatus, 5/15/20-6/1/20, to correspond with USM's 2 sessions

# Findings

```{r}

FM_Orig <- read.csv("file:///Z:/DAA/Marketing/MKT_output.csv", header = T, stringsAsFactors = F)
```


```{r}
wrongAds <- c("SU20_IG_DISP_ALL_SIC_S_1", "SU20_IG_DISP_ALL_SIC_S_2", "SU20_IG_DISP_ALL_SIC_S_3")
```


```{r}
FM_Orig <- FM_Orig %>% 
  mutate(Code_Vendor =  ifelse(Master_Adname %in% wrongAds, "FB", Code_Vendor), 
         Code_Medium = ifelse(Master_Adname %in% wrongAds, "DISP", Code_Medium), 
         Code_Product = ifelse(Code_Product == "S", Code_Audience, Code_Product), 
         Code_Audience = ifelse(Master_Adname %in% wrongAds, "ALL", Code_Audience),
         Code_Adnumber = ifelse(Master_Adname %in% wrongAds, Code_Interactivity, Code_Adnumber),
         Code_Adnumber = ifelse(Master_Adname == "FA21_IG_DISP_ALL_CGCY_S__1", 1,ifelse(Master_Adname == "FA21_IG_DISP_ALL_CGCY_S__2", 2, ifelse(Master_Adname=="FA21_IG_DISP_ALL_CGCY_S__3", 3, ifelse(Master_Adname =="FA21_IG_DISP_ALL_CGCY_S__4",4,Code_Adnumber)))), Code_Interactivity = ifelse(Master_Adname %in% wrongAds, "S", Code_Interactivity) )

```

```{r eval=FALSE, include=FALSE}
unique(names$Master_Adname)
names <- FMNew %>%
  group_by(Master_Adname) %>% summarise(I = sum(Master_Impressions), P = sum(Master_Unique_Pageviews))
names
```



```{r}
FM_Orig <- FM_Orig %>% 
  filter(Code_Product == "SIC" & Code_RecruitingPeriod == "SU20") %>% 
  rename(
  Term = Code_RecruitingPeriod, 
  Audience = Code_Audience, 
  Product = Code_Product, 
  Date = Master_Date
                              )
```




```{r data 1}

FM <- FM_Orig %>% filter(Master_Adname_Type == "NC" )
FM <- FM %>% 
  mutate(Audience = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1", "TL", Audience), 
         Product = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1", "UG", Product), 
         Term = ifelse(Term == " FA20", "FA20", Term)) %>%
  select(1:8, 13, 15:19, 21:24, 26:29, 31:39, 41) %>% 
  select(Date, Master_Landing_Page,everything())
#FM <- FM %>% mutate_at(9:30, ~replace(., is.na(.), 0)) %>% mutate(Date = as.Date(Date, format = "%m/%d/%Y")) %>% arrange(Date)

FM <- FM %>% 
  mutate_at(10:31, ~replace(., is.na(.), 0)) %>% 
  mutate(Date = as.Date(Date, format = "%Y-%m-%d"), 
         Master_Results = as.numeric(Master_Results), 
         Master_Engagements = as.numeric(Master_Engagements)
         #,
         #Product = ifelse(Product == "TL", "TR", Product)
         ) %>% 
  arrange(Date) %>% 
  filter(Date > "2019-08-15")




FM <- FM %>% mutate(Master_Landing_Page_1 =
                      ifelse(grepl("advance", Master_Landing_Page), "/advance", 
                             ifelse(grepl("here", Master_Landing_Page), "/here",
                                    ifelse(grepl("excel", Master_Landing_Page), "/excel",
                                           ifelse(grepl("regional", Master_Landing_Page), "/NEBBHE", 
                                                  ifelse(grepl("cyber", Master_Landing_Page), "/cyber-security", 
                                                         ifelse(grepl("muskie", Master_Landing_Page), "/muskie",
                                                                ifelse(grepl("", Master_Landing_Page), "/blank",
               ifelse(grepl("visit", Master_Landing_Page), "/visit","/other"
                    ))))))))) %>% select(Date, Master_Landing_Page, Master_Landing_Page_1, everything())

```

```{r data 3}

colorP <- c("#F6A704", "#0E1033","#4E7B14","#A92007","#D47E0A")
 FMVM <- FM %>%
   mutate(Product_Audience = paste0(Product, "_", Audience)) %>%
   group_by(Term, Audience,Product, Code_Vendor, Code_Medium,Date) %>%
   summarise(
     Cost = round(sum(Master_Cost), 2),
     Clicks = sum(Master_Clicks),
     Impressions = round(sum(Master_Impressions),0),
     #CTR = paste0(round(Clicks/Impressions * 100, 2), "%"),
     Bounces = sum(Master_Bounces),
     Sessions = sum(Master_Sessions),
     UPV = sum(Master_Unique_Pageviews),
     Views = sum(Master_Views),
     Completions = sum(Master_Completions),
     Master_Time_On_Page = sum(Master_Time_On_Page), 
     Master_Pageviews = sum(Master_Pageviews), 
     Master_Exits = sum(Master_Exits), 
     #BounceRate = paste0(round(Bounces/Sessions * 100, 2), "%"),
     Step1 = sum(Master_Time_On_Page)/(sum(Master_Pageviews)- sum(Master_Exits)),
     Av_TOP = round_hms(as_hms(Step1), 5),
     CTR = round(Clicks/Impressions * 100, 2),
     BR = round(Bounces/Sessions * 100, 2),
     ViewRate = round(Views/Impressions * 100, 2),
     VTR = round(Completions/Impressions * 100, 2),
     ClickableCompletions = sum(Master_Clickable_Completions),
     ClickableCompRate = round(Clicks/ClickableCompletions * 100, 2), 
     Swipes = sum(Master_Swipes), 
     SwipeUpRatePct = round(Swipes/Impressions * 100, 2),
     Opens = sum(Master_Clicks_To_Site),
     CTOR = round(Opens/Clicks * 100, 2), 
     Sends = sum(Master_Sends), 
     LIOpens = sum(Master_Opens),
     LIClicks = sum(Master_Clicks_Sponsored_InMail),
     OpenRate = round(LIOpens/Sends * 100, 2), 
     Engagements = sum(Master_Engagements),
     Results = sum(Master_Results), 
     EngagementRate = round(Engagements/Impressions * 100, 2),
     EngRate = round((sum(LIOpens)+sum(Engagements))/sum(Sends)*100, 2), 
     Avg_RR = round(sum(Results)/sum(Impressions) * 100, 2),
     LICTOR = round(sum(LIClicks)/sum(LIOpens) * 100, 2)) %>%
   select(Date, Impressions, Clicks, Bounces, Sessions, Swipes, CTR, SwipeUpRatePct, UPV, BR, Av_TOP, ClickableCompRate, VTR, CTOR,OpenRate, Sends, ViewRate, ClickableCompletions, Completions, Opens, LIOpens, LIClicks, Engagements, LICTOR, EngRate, EngagementRate, Master_Exits, Master_Pageviews, Master_Time_On_Page, Cost, Avg_RR, Results, Views, Completions)
 
desiredRecruiting <- c("FA20", "FA21", "SU20")

```


### Facebook Display

```{r fig.height=1.5, fig.width=8}
data1 <- FMVM %>% 
  filter( Code_Medium == "DISP" & Code_Vendor == "FB" & Term %in% desiredRecruiting & Impressions > 0 & Date < "2020-06-02" ) %>% 
  group_by(Term, Product, Audience,Date) %>% 
  summarise(
    Impressions = sum(Impressions),
    Cost = sum(Cost),
    #Results = sum(Results),
    CTR = Clicks/Impressions,
    UPV = sum(UPV),
    BR = Bounces/Sessions,
    # OpenRate = LIOpens/Sends, 
    # EngagementRate = Engagements/Impressions,
    # BR = Bounces/Sessions, 
    # ResultsRate = Results/Impressions, 
    # ViewRate = round(Views/Impressions * 100, 2),
    # VTR = round(Completions/Impressions *100, 2) 
    )
kable(data1 %>% group_by(Term, Product) %>% summarise(
  Impressions = prettyNum(sum(Impressions), big.mark = "," ),
  
  CTR = paste0(round(mean(CTR) *100, 2), "%"),
  UPV = prettyNum(sum(UPV), big.mark = "," ),
  
  BR = paste0(round(mean(BR) *100, 2), "%"), 
  Cost = paste0("$",prettyNum(sum(Cost), big.mark = ","), ".00") ))
```


```{r fig.height=1.5, fig.width=8}
PGCTR <- data1 %>%  
    ggplot(aes(x = Date, y = CTR*100)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = c(0.45, 0.72), linetype="dashed") + ylab("CTR")
  
  PGImp <- data1 %>% 
    ggplot(aes(x = Date, y = Impressions )) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) +  scale_fill_manual(values=c("#9999CC"))
  
  
  PGUPV <- data1 %>% 
    ggplot(aes(x = Date, y = UPV)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+  scale_fill_manual(values=c("#9999CC"))
  
  
  
  PGBR <- data1 %>% 
    ggplot(aes(x = Date, y = BR)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+  scale_fill_manual(values=c("#9999CC"))
  
  
  a <-  ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  # annotate_figure(a, text_grob(paste0(data1$Term, "_ ", data1$Product, "_Facebook"), color = "darkblue", face = "plain", size = 18, just = "right"))
  
 a 
  
```

---

### Instagram Display

```{r}
data2 <- FMVM %>% 
  filter( Code_Medium == "DISP" & Code_Vendor == "IG" & Term %in% desiredRecruiting & Impressions > 0 ) %>% 
  group_by(Term, Product, Audience,Date) %>% 
  summarise(
    Impressions = sum(Impressions),
    Cost = sum(Cost),
    #Results = sum(Results),
    CTR = Clicks/Impressions,
    UPV = sum(UPV),
    BR = Bounces/Sessions,
    # OpenRate = LIOpens/Sends, 
    # EngagementRate = Engagements/Impressions,
    # BR = Bounces/Sessions, 
    # ResultsRate = Results/Impressions, 
    # ViewRate = round(Views/Impressions * 100, 2),
    # VTR = round(Completions/Impressions *100, 2) 
    )

kable(data2 %>% group_by(Term, Product) %>% summarise(
  Impressions = prettyNum(sum(Impressions), big.mark = "," ),
  
  CTR = paste0(round(mean(CTR) *100, 2), "%"),
  UPV = prettyNum(sum(UPV), big.mark = "," ),
  
  BR = paste0(round(mean(BR) *100, 2), "%"), 
  Cost = paste0("$",prettyNum(sum(Cost), big.mark = ",")) ))
```



```{r fig.height=1.5, fig.width=8}
PGCTR <- data2 %>%  
    ggplot(aes(x = Date, y = CTR*100)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.16, linetype="dashed") +  ylab("CTR")
  
  PGImp <- data2 %>% 
    ggplot(aes(x = Date, y = Impressions )) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) +  scale_fill_manual(values=c("#9999CC"))
  
  
  PGUPV <- data2 %>% 
    ggplot(aes(x = Date, y = UPV)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+  scale_fill_manual(values=c("#9999CC"))
  
  
  
  PGBR <- data2 %>% 
    ggplot(aes(x = Date, y = BR * 100)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+ ylab("BR")
  
  
  a <-  ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  # annotate_figure(a, text_grob(paste0(data2$Term, "_ ", data2$Product, "_ ", data2$Audience, " "), color = "darkblue", face = "plain", size = 18, just = "right"))
  # 
 a 
  
```

---

#

#

### Optimized Display

```{r fig.height=1.5, fig.width=8}
data3 <- FMVM %>% 
  filter( Code_Medium == "DISP" & Code_Vendor == "FB" & Term %in% desiredRecruiting & Impressions > 0 & Date > "2020-06-02" ) %>% 
  group_by(Term, Product, Audience,Date) %>% 
  summarise(
    Impressions = sum(Impressions),
    Cost = sum(Cost),
    #Results = sum(Results),
    CTR = Clicks/Impressions,
    UPV = sum(UPV),
    BR = Bounces/Sessions,
    # OpenRate = LIOpens/Sends, 
    # EngagementRate = Engagements/Impressions,
    # BR = Bounces/Sessions, 
    # ResultsRate = Results/Impressions, 
    # ViewRate = round(Views/Impressions * 100, 2),
    # VTR = round(Completions/Impressions *100, 2) 
    )
kable(data3 %>% group_by(Term, Product) %>% summarise(
  Impressions = prettyNum(sum(Impressions), big.mark = "," ),
  
  CTR = paste0(round(mean(CTR) *100, 2), "%"),
  UPV = prettyNum(sum(UPV), big.mark = "," ),
  
  BR = paste0(round(mean(BR) *100, 2), "%"), 
  Cost = paste0("$",prettyNum(sum(Cost), big.mark = ",")) ))
```


```{r fig.height=1.5, fig.width=8}
PGCTR <- data3 %>%  
    ggplot(aes(x = Date, y = CTR*100)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = c(0.45, 0.72), linetype="dashed") + ylab("CTR")
  
  PGImp <- data3 %>% 
    ggplot(aes(x = Date, y = Impressions )) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) +  scale_fill_manual(values=c("#9999CC"))
  
  
  PGUPV <- data3 %>% 
    ggplot(aes(x = Date, y = UPV)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+  scale_fill_manual(values=c("#9999CC"))
  
  
  
  PGBR <- data3 %>% 
    ggplot(aes(x = Date, y = BR)) +
    geom_line(color = "#323DA5") +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+  scale_fill_manual(values=c("#9999CC"))
  
  
  a <-  ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  a
  # annotate_figure(a, text_grob(paste0(data1$Term, "_ ", data1$Product, "_ ", data1$Audience, " "), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
```

### AdWords CPC

```{r fig.height=1.5, fig.width=8}

adWords <- read.csv("C:/Users/christine.iyer/Box/SpecialProjects/FY20_SummerCourses/FY20_SUMMER.csv", header = T, stringsAsFactors = F)


adWords <- adWords %>% filter(Source == "Google") %>%
  mutate(
    Date = as.Date(Week.of.Date, format = "%d-%b-%y"),
    Time.on.Page = as.numeric(gsub("\\,", "", Time.on.Page)), 
    Pageviews = as.numeric(gsub("\\,", "", Pageviews)), 
    Impressions = as.numeric(gsub("\\,", "", Impressions))) %>% 
  mutate_at(5:14, ~replace(., is.na(.), 0)) %>% 
group_by(Date, Source) %>% summarise_at(vars(Bounces:Impressions), sum) %>% 
  mutate(
    
    CTR = round(Clicks/Impressions*100,2), 
    BR = round(Bounces/Sessions*100,2), 
    Step1 = Time.on.Page/(Pageviews- Exits),
    Av_TOP = round_hms(as_hms(Step1), 5)) %>% select(Source, Av_TOP,everything())
#%>% 
a <- ggplot(adWords, aes(x= Date, y = CTR))+ geom_line(color = "#323DA5")+theme_bw()+geom_hline(yintercept = c(1), linetype="dashed")+ 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
b <- ggplot(adWords, aes(x= Date, y = Impressions))+ geom_line(color = "#323DA5")+theme_bw()+ 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
c <- ggplot(adWords, aes(x= Date, y = Unique.Pageviews))+ geom_line(color = "#323DA5")+theme_bw()+ 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
d <- ggplot(adWords, aes(x= Date, y = BR))+ geom_line(color = "#323DA5")+theme_bw()+ 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())

a <-  ggarrange(b, a,c, d, ncol=4, nrow=1, common.legend = TRUE, legend="right")

#kable(adWords)

newAW <- adWords %>%
  group_by(Source) %>% 
summarise_at(vars(Bounces:Step1), sum) %>%
        
        mutate(
  
  
  CTR = paste0(round(sum(Clicks)/sum(Impressions)*100,2), "%"),
  UPV = prettyNum(sum(Unique.Pageviews), big.mark = "," ),
  
  BR = paste0(round(sum(Bounces)/sum(Sessions)*100,2), "%"), 
  Cost = paste0("$",prettyNum(sum(Cost), big.mark = ",")),
  Step1 = (sum(Time.on.Page)/(sum(Pageviews)- sum(Exits))),
     Av_TOP = round_hms(as_hms(Step1), 5),
  Impressions = prettyNum(Impressions, big.mark = "," )) %>% 
    select(Source,Impressions, CTR, UPV, BR, Av_TOP, Cost)
kable(newAW)

a
```


# Conclusions

